Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-24 article.tex
cleaned up notes etc

\usepackage{graphicx}

@@

%%%%%%%%%%%%%%%%
% Working title
%
\title{Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards}

@@

\section{Introduction}

@@

% TODO: review the following questions:
What are the key factors/indicators of environmental sustainability in the australian winegrowing industry?
How can we measure and relate the factors that contribute to sustainability in the australian winegrowing industry?
What are the key factors that relate directly to environmental sustainability?
- and what in turn are the factors that contribute to these (and thus indirectly to environmental sustainability)?

% Things to consider
%
% Why is the knowledge important?
This was identified as a gap within our own prior research and is helpful in creating a basis for scenario assessment and comparison. This will allow a greater understanding of how these factors change within different scenarios; whether that be climate, region, business goal.
% What is the significance?
The significance is to bridge the gap between correlations and data to causal relationships. To inform growers using factors that are within their control, or how factors within their control are indfuenced by natural phenomenon.
% How will the findings be utilised?
These findings will be used to help inform the wider winegrowing community of what factors are most significant to environmental outcomes, and how they interact with one another. In practice this study aids a grower through informing them of how decisions impact environmental outcomes and how changing circumstance contribute to these factors and outcomes.
% What improvements may be derived from this result?
A wider more informed understanding of contributing factors to environmental impact and how different factors relate to one another to contribute to these findings.
% Are the terms well defined?
The terms are well defined. This was a key outcome of this project.
% Do experts think your question is important/relevant/doable?
Experts helped to guide this decision, and changed the trajectory of this project in response to data presented and how well they believed they could inform the study.

% What is the nature of your question?
%         who, what, where, when, why, how?
What are the key factors that contribute to environmental impact within the Australian winegrowing industry?
How do these key factors relate to each other and what are the factors that influence them?
What are the decision that can be made by growers that can change the environmental outcomes of their vineyards?
How do these factors chagne across well understood scenarios?
% You can have more than one question.

% What is the most important question your paper will pose?
What are the key factors to environmental impact within the Australian winegrowing industry, and how are these factors related?
% NB It is essential that your answer is framed as a direct question.  Your response must end with a question mark.

% Why is the question/issue/problem worth examining?
By examining the key and relevant factors to vineyards' environmental impacts we can better prepare for future changes in climate pressure, economic restrictions; that is we can better use this model to assess the potential environmental outcomes of the wine industry, as informed by experts, given potential upcoming challenges or changes.
% Briefly outline the problem you are tackling and explain why the problem is important to knowledge in general.  “Nothing much is known” is not sufficient justification by itself.  You have to show why the gap in knowledge is important.  Expect to draw heavily on your reading of the literature in framing your answer but do not get into detail of  author and year.
The collection of data and subsequent statistical analytics can only go so far as to fill the gap between cause and effects within wiengrowing. This research helps to fully understand the relevant decisions being made, how they are informed and what the known outcomes are. This helps to align these results to data collected to show stronger causal relationships than pure correlative, or hypothetical postulations of statistical analysis.
%%%%%%%%%%
% Answer %
%%%%%%%%%%

@@

@@

\subsection{Literature Review}
#TODO:

@@

The calculations of a Bayesian Network are based on Bayes' theorem, shown as follows
\begin{equation}\label{bayesformula}
P(A|B)= {P(B|A)P(A)}\over{P(B)}
\end{equation}.
Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}. Within a Bayesian Network, an event can be considered any given node and its outcome one of the node's classes. Events are connected by edges within the network, with each node containing the probability of an outcome given parent nodes' outcomes. This is an iterative application of \ref{bayesformula}, which can be achieved through

@@

$$ y = {{p(a, e)(x)}\over{p(e)(x)}}={{\alpha x + \beta}\over{\gamma x + \delta}} $$.

@@

% FIXME: should I extrapolate on this method?

@@

Due to the regional limitations of the model experts proposed a case study of a specific and well understood region: Coonawarra in South Australia. The choice of the region was due to the prevalence of data within and around the region, as well as experts' understanding of the region's unique challenges and benefits to winegrowing. The Coonawarra model was built off of the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel.

@@

Transparency with the expert panel was a key ingredient with this approach, highlighting explicitly what these problems were and how we would overcome them. This included agreeing upon definitions of each node before connecting edges between them.

Although originally multiclass nodes existed, the bayesian network was altered to only include binary class nodes. Each edge between a node had to answer the following questions:
\begin{enumerate}
        \item Are the nodes in the BN the right ones?
        % \item Are the state spaces (values) for each node correct?
        \item Are the arcs right?
\end{enumerate}
If the answer to any of the above questions was no; then the structure was not considered sufficiently defined. Although we explicitly defined the structure of the BN prior to CPT parametarisation. This process continued when adding conditionaly probability values. The entire process of construction iinvolved the steps:
\begin{enumerate}
        \item exposing the panel to a strawman argument/model/definition
        \item Outlining the model and the process involved in defining the structure of a BN
        \item The expert panel reviewing possible nodes and arcs and definitions
        \item Defining their own structure, node or term.
        \item Agreeing upon the final definition, structure or model.
\end{enumerate}
\subsubsection{Trying to build the full model all at once}

Korb & Nicholson say that it is nearly impossible to build a complex BN all in one go. They recommend:
\begin{enumerate}
        \item dividing models into subcomponents
        \item breaking down the problem into a single target variable
        \item reducing the scope of the problem
        \item Setting a single time frame for the problem
\end{enumerate}
The strawman was presented as three subcomponents that pertained to the triple bottom line's environment, economy and social aspects.
Within the first workshop it was agreed on by the expert panel to reduce the scope from a triple bottom line to only reviewing the environmental impacts of vineyards. This also reduced the BN to a single terminal node. It was further decided to create the BN as a single season to limit its complexity.

\subsection{The problem}
\subsubsection{Not understanding the problem context, complexity without value.}
It is crucial to gain a clear understanding of the problem and its context. This can be seen as answering the following questions:
\begin{enumerate}
        \item what do you want to reason about?
        \item What dont you know?
        \item What information do you have?
        \item What do you know?
These questions are well addressed in prior research. The creation of baseline models showed strong linear relationships between many variables. The creation of XGBoosted trees uncovered the ability to well inform any particular variable but with no real causal structure or understandability. here we seek to pursue causality and link these variables together in a way that is more aligned with a decision support structure than purely as a predictive exercise.
\subsubsection{Complexity without value}
A very common impulse, when something is known about the problem, is to want to put it in the model. But including everything known, just because it is known, simply adds complexity to the model without adding any value (and in fact often reduces value). Instead, the knowledge engineer must focus on the problem:
"Which of the known variables are most relevant to the problem?"
- This issue in its the simplest form has attempted to be overcome through trying to mediate the workshop and inform experts of the potential probelsm that will come with a cumbersome model.
\end{enumerate}

\subsection{Structure - Nodes}
The list below is each of the problems, which can be addressed together in some fashion as the approaches of solving them overlap.
\begin{enumerate}
        \item Getting the node values wrong
        \item Node values aren't exhaustive
        \item Node values aren't mutually exclusive
        \item Incorrect modelling of mutually exclusive outcomes
        \item Trying to model fuzzy categories
        \item Confusing state and Probability
        \item Confusion about what the node represents
\end{enumerate}
Two major strategies were employed to overcome these problems. Tying nodes explicitly to a data source that corroborated the definition and state in some manner as the node. For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.

\subsection{Structure Arcs}
\subsubsection{Getting the arc directions wrong}
Arc directions are commonly wrong for the following reasons:
\begin{enumerate}
        \item Modelling reasoning rather than causation
        \item Inverting cause and effect
        \item Missing variables
\end{enumerate}
To note: Korb and Nicholson do not actually suggest a method for overcoming these problems. There is an inherint risk in creating a model and not having knowledge of a missing variable or of a causation. It is important to acknowledge that there is always a possibility that causation is mixed up with reasoning, and that not all variables are always known.
\subsubsection{Too many parents}
Sometimes it is unavoidable that a node is affected by many factors, or other nodes. There are some methods to help overcome this such as divorcing, in which a node is created to capture the cumulative affects of several parents on a child. This technique was employed in the creation of the structure of the BN with the expert panel.

\subsection{Parameters}
\subsubsection{Experts estimates of probabilities are biased}
\begin{enumerate}
        \item Overconfidence: The attribution of higher than justifiable probabilities to nodes/events.
        \indent The tendency to attribute higher than justifiable probabilities (\citep{lichtensteinCalibrationProbabilitiesState1982} 
        \item Anchoring: The tendency towards higher/lower based off of an arbitrary point of comparison. "Anchoring" people at a higher or lower than normal prediction because of some assumption or example  \citep{kahnemanPsychologyPrediction1973}.
        \item Availability: The assessing of an event as more probable than is justifiable becaues it is more memorable or noticeable \citep{tverskyJudgmentUncertaintyHeuristics1974}.

\end{enumerate}
We have attempted to overcome this with two methods. A diverse and varried expert panel. Those participanting have experience in multiple vineyards as managers and other duties as well as the panel itself having varied manager/owners from different regions and scale. With some experts being more specialised in specific areas such as agro-chemicals.
\subsubsection{Inconsistent probabilities}
The collection of probabilities for when the CPT is large can result in inconsistent probabilities. The collection of probabilities at different times or if probabilities are supplied by different experts can result in inconsistent probabilities as well.
The use of desciptors such as very high or low can be of assistance \cite{vandergaag2013elicit}. In this study we overcame this through the use of worded response such as high and low. We then assigned probabilities to those broader cases. We had every expert agree upon each of the probabilities so that they could argue for or against any particular bias and so that the probabilities would even out to a more broader applicability, across all of the experts experiences.
% \item Inconsistent "filling in" of large CPTs:
-       -       - Being dead certain.
\subsubsection{Incoherent probabilities (not summing to 1)}
We used software that automatically detected incoherent probabilities when filling in the CPT values to overocme this problem.
\subsubsection{Being dead certain}
It is important that we limit over confidence (A quote form mark twain was used in the korb and Nicholson). 
Our best defence against this was to use multiple experts with different experiences and to challenge them when something was certain. To ask why and to check in about their thoughts.

\citep{morganUncertaintyGuideDealing1990}
Two attributes of good elicitation process are:
\begin{enumerate}
        \item The expert should be apprised of what is known about the process, especially the nearly universal tendency to overcomefidence and other forms of bias. In order to avoid some problems, values should be elicited in random order and the expert not given feedback on how the different values fit together until a complet set has been elicited.
        \item The elicitation process is not simply one of requesting and recording numbers but also one of the refining the definitions of variables and terms to be used in the model. What values are elicited depends directly upon the interpretation of terms and these should be made as explicit as possible and recorded during the elicitation. This is part of the process management described earlier.
\end{enumerate}
-

\citep{Boneh2021} Boneh, T. (2010). Ontology and Bayesian decision networks for supporting the meterological forecasting process. Ph. D thesis, Clayton School of infomration technology, Monash university
Boneh 2010 describe Knowledge Engineering with Bayesian Networks (KEBN) as occurring in a 4 stage life cycle:
- Bayesian Network Structure
- Probability Parameters
- Decision Structure
- Utilities Preference

Pitchforth \citep{pitchforthProposedValidationFramework2013} agrees with this style of structure naming these steps as:
- Structure
- Discretisation
- Parametarisation
- Model behaviour
- Validation

Korb & Nicholson have a similar view to Pitchforth. utilising a waterfall style developemental approach which include 5 stages:
- Building the BN
-       - Structure
-       - Parameters
-       - Preferences
- Validation
-       - Sensitivity Analysis
-       - Accuracy testing
- Field testing
-       - Alpha/Beta testing
-       - Acceptance testing
- Industrial use
-       - Collection of Statistics
- Refinement
-       - Updating procedures
-       - Regression testing

Where discretisation and validation are additional steps to assign intervals to continuous factors (discretisation) and to ensure the models appropriateness (validation)

With validation incorporating the expert scrutiny of the models begaviour for scenarios, as well as comparing this to both data and other literature.

\subsection{Structure and Conditional Probabilities}

\citep{korbBayesianArtificialIntelligence2011}

% Abstract

1. Introduction to Methodology

    Brief overview of the research approach and the rationale behind using a Bayesian Network (BN) model for sustainability assessment in viticulture.
    Mention of the collaborative expert elicitation process and the sequential workshops that shaped the model development.

2. Identification of Sustainability Indicators

    Description of the process for selecting sustainability indicators, including the use of data from Sustainable Wine Australia.
    Criteria for indicator selection, focusing on relevance to environmental, economic, and social dimensions of sustainability in winegrowing.

3. Expert Elicitation Process

    Overview of the expert panel composition and the expertise represented.
    Objectives and structure of the expert elicitation process, highlighting the series of workshops conducted.

Workshop 1: Variable Review and Straw Man Model Introduction

    Objectives: To agree on the sustainability indicators and introduce the initial straw man model.
    Activities: Discussion on indicator relevance and definitions; presentation of the straw man model.
    Outcomes: Agreement on initial set of variables and conceptual understanding of the model's direction.

Workshop 2: Model Structure Refinement and Interpolation Method Introduction

    Objectives: To refine the model's structure and address the complexity of CPTs through an interpolation method.
    Activities: Examination of variable relationships; identification of complex CPTs; proposal of the linear interpolation method.
    Outcomes: Revised model structure; decision to develop and implement the interpolation method for complex CPTs.

Workshop 3: Finalization of CPTs and Case Study Selection

    Objectives: To finalize CPT values using the interpolation method and select a case study for model application.
    Activities: Presentation and application of the interpolation method; finalization of CPT values; selection of the Coonawarra wine region for the case study.
    Outcomes: Completion of model parameterization; selection of case study region emphasizing the model's practical application.

4. Development and Implementation of the Interpolation Method

    Detailed explanation of the linear interpolation method developed to manage the complexity of CPTs for variables with extensive connections.
    Justification for choosing this method and its anticipated impact on the model's usability and accuracy.

5. Case Study Application: Coonawarra Wine Region

    Rationale for selecting the Coonawarra wine region as a case study to apply and test the BN model.
    Brief description of how the model was applied to this specific context, including any regional data used and adjustments made for the case study.

6. Model Validation

    Overview of the validation process employed to ensure the accuracy and reliability of the BN model.
    Description of internal and external validation measures, including expert review and comparison with independent datasets.

7. Conclusion

    Summary of the methodological approach, emphasizing the collaborative expert elicitation process and the innovative solutions developed for model construction and parameterization.
    Brief mention of the significance of the methodology for sustainability assessment in viticulture and potential implications for future research and practice.

@@

>>>>

\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}

\lstset{
  basicstyle=\ttfamily,
  frame=single,
  backgroundcolor=\color{lightgray!20},
  keywordstyle=\color{blue},
  commentstyle=\color{gray},
  stringstyle=\color{green},
  showstringspaces=false
}

@@

%%%%%%%%%%%%%%%%
% Working title
%

% \section{Preamble notes}

@@

@@

% Things to consider
%
% Why is the knowledge important?
% This was identified as a gap within our own prior research and is helpful in creating a basis for scenario assessment and comparison. This will allow a greater understanding of how these factors change within different scenarios; whether that be climate, region, business goal.
% % What is the significance?
% The significance is to bridge the gap between correlations and data to causal relationships. To inform growers using factors that are within their control, or how factors within their control are indfuenced by natural phenomenon.
% % How will the findings be utilised?
% These findings will be used to help inform the wider winegrowing community of what factors are most significant to environmental outcomes, and how they interact with one another. In practice this study aids a grower through informing them of how decisions impact environmental outcomes and how changing circumstance contribute to these factors and outcomes.
% % What improvements may be derived from this result?
% A wider more informed understanding of contributing factors to environmental impact and how different factors relate to one another to contribute to these findings.
% % Are the terms well defined?
% The terms are well defined. This was a key outcome of this project.
% % Do experts think your question is important/relevant/doable?
% Experts helped to guide this decision, and changed the trajectory of this project in response to data presented and how well they believed they could inform the study.

% % What is the nature of your question?
% %         who, what, where, when, why, how?
% What are the key factors that contribute to environmental impact within the Australian winegrowing industry?
% How do these key factors relate to each other and what are the factors that influence them?
% What are the decision that can be made by growers that can change the environmental outcomes of their vineyards?
% How do these factors chagne across well understood scenarios?
% % You can have more than one question.

% % What is the most important question your paper will pose?
% What are the key factors to environmental impact within the Australian winegrowing industry, and how are these factors related?
% % NB It is essential that your answer is framed as a direct question.  Your response must end with a question mark.

% % Why is the question/issue/problem worth examining?
% By examining the key and relevant factors to vineyards' environmental impacts we can better prepare for future changes in climate pressure, economic restrictions; that is we can better use this model to assess the potential environmental outcomes of the wine industry, as informed by experts, given potential upcoming challenges or changes.
% % Briefly outline the problem you are tackling and explain why the problem is important to knowledge in general.  “Nothing much is known” is not sufficient justification by itself.  You have to show why the gap in knowledge is important.  Expect to draw heavily on your reading of the literature in framing your answer but do not get into detail of  author and year.
% The collection of data and subsequent statistical analytics can only go so far as to fill the gap between cause and effects within wiengrowing. This research helps to fully understand the relevant decisions being made, how they are informed and what the known outcomes are. This helps to align these results to data collected to show stronger causal relationships than pure correlative, or hypothetical postulations of statistical analysis.
%%%%%%%%%%
% Answer %
%%%%%%%%%%

@@

\section{Introduction}
TODO: refs
The imperative for environmental sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation. This is especially true for Viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries. This study investigates environmental sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs). A broader model of Australian winegrowing was created, with a more specific case study looking at the Coonawarra winegrowing region being conducted to create a rigorous and quantitative approach to understanding sustainable practices and the relationships between these factors.

Bayesian Networks are probabilistic models that effectively capture and analyse the interactions between multiple factors in complex systems. By integrating expert knowledge and region-specific data, BNs were able to provide a structured framework to quantify the impacts of various factors on sustainability within Australian winegrowing. This methodology not only shed light on current sustainability practices but also identified critical areas for intervention through illustrating the interconnectedness of each of the factors and how they directly or indirectly influence one another.

This research is guided by several fundamental inquiries aimed at enhancing our understanding of environmental sustainability in viticulture. a primary question is how key factors impacting environmental sustainability can be rigorously defined and quantified. Another focus delves into identifying the unique regional characteristics of different regions, using the Coonawarra winegrowing region to illustrate how factors influence might change regionally. Additionally, the study investigates how these factors interact within a Bayesian Network model, providing a framework for understanding their complex interdependencies. The final question, looks at how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge.

The industry panel was used as a catalyst in the early stages of this research to help explore these multifaceted questions. A comprehensive literature review was compiled through both structured searches. This extensive review established a foundational understanding of the current knowledge landscape and identified major concepts within sustainable winegrowing. To ensure a robust and comprehensive approach, a combination of qualitative and quantitative methods were employed within the creation of the BN; this included expert consultations and data analysis, which were instrumental in the BNs construction and validation. The consultations were done through the use of An industry panel comprising experts in viticulture and environmental sustainability, which provided insights and guidance throughout the research process. Their expertise was crucial in defining and quantifying the key factors, and further understanding the specific regional characteristics to Coonawarra. Through the integration of industry knowledge and academic research this study aimed to produce findings that are not only theoretically sound but also practically relevant and applicable to the viticulture industry.

% The results section presents an in-depth analysis of The Coonawarra case study, highlighted significant factors identified by the BN and their interactions. Key factors such as water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions were found to be the most influential on environmental sustainability in the region. Comparative analysis with another case study BN and existing literature underscores the robustness and relevance of our findings.

This study provides critical insight into enhancing environmental sustainability through informed decision-making and targeted interventions by highlighting the sensitivity of different factors to the environmental sustainability of vineyards. The findings have significant implications for the local viticulture industry and offer a replicable framework for other agricultural sectors aiming to achieve sustainability.

@@

\subsection{Literature Review}

The literature review was a crucial component of this study, designed to establish a comprehensive understanding of existing knowledge on environmental sustainability in viticulture. The review aimed to identify key factors influencing sustainability, understanding their interactions, and to compare findings with the results obtained from the Bayesian Network and expert definitions.

A systematic search strategy was employed to ensure a thorough review of the literature. The search included multiple academic journals; with search terms being broadly based on key factors given from the industry panel. This approach was used capture a wide range of relevant literature, incorporating keywords associated with viticulture, sustainability, and other agricultural operations related to the definitions provided by the expert panel. The general query (adapted to different formats for various journals and bibliographic databases) used for the literature search was:

% This is the query in a code-like format.
\begin{lstlisting}[language=]
    (Water OR Agrochemical OR Chemical OR Ground management OR Pest OR Disease OR Management OR Electricity OR Energy OR GHG OR Emissions OR Greenhouse gas emissions OR Environmental OR Environment OR Ecological OR Fertiliser OR Fertilizer OR Fuel OR Biofuel OR Price OR Nutrient OR Runoff OR Leeching OR Market OR Supply and demand OR Soil OR Organic carbon OR SOC OR Tractor OR Field OR Operations OR Weather OR Climate OR Yield OR Production)
    AND
    (Sustainability OR Sustainable OR Eco-friendly OR Environmentally friendly OR Green practices)
    AND
    (Viticulture OR Winegrowing OR Vineyard)
    \end{lstlisting}
Inclusion and Exclusion Criteria

To ensure the relevance and quality of the literature reviewed, specific inclusion and exclusion criteria were applied. Articles were only excluded if they were not available in full text or were not written in English. Journals beyond those included were also examined especially where they offered in-depth reviews of sustainability within agriculture or winegrowing; methodological reviews within this context were also included.

Once relevant articles were identified, data extraction was conducted to gather information on the key factors influencing environmental sustainability in viticulture, their interactions, and the methodologies used in previous studies. The extracted data was then processed using Leximancer to identify common themes and concepts in the existing literature.

An expert panel comprising specialists in viticulture and environmental sustainability was engaged throughout the literature review process. The panel provided guidance on the selection of relevant articles, helped refine the inclusion criteria through their list of key factors. By conducting a thorough literature review, this study aimed to build a solid foundation of existing knowledge, identify gaps, and position the findings from the Bayesian Network models within the broader context of sustainability research in viticulture. This approach ensured that the study's results were not only robust and scientifically sound but also practically relevant and actionable for industry stakeholders.

@@

The calculations of a Bayesian Network are based on Bayes' theorem, shown as follows
\begin{equation}\label{bayesformula}
P(A|B)= {P(B|A)P(A)}\over{P(B)}
\end{equation}.

Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}. Within a Bayesian Network, an event can be considered any given node and its outcome one of the node's classes. Events are connected by edges within the network, with each node containing the probability of an outcome given parent nodes' outcomes. This is an iterative application of \ref{bayesformula}, which can be achieved through

@@

\begin{equation}
y = {{p(a, e)(x)}\over{p(e)(x)}}={{\alpha x + \beta}\over{\gamma x + \delta}}
\end{equation}.

@@

% should I extrapolate on this method?

@@

Due to the regional limitations of the model, experts proposed a case study of a specific and well understood region: Coonawarra in South Australia. The choice of the region was due to the prevalence of data within and around the region, as well as experts' understanding of the region's unique challenges and benefits to winegrowing. The Coonawarra BN was built off of the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel. Difference in factor interactions were further discussed by the panel, resulting in two distinct BN models that influenced two types of approaches; primarily differing between opportunity based tractor use for undervine operations and more purposeful undervine management, as well as the inclusion of further soil based factors that could be significant for particular sites.

% \subsection{Methods notes}

@@

% Transparency with the expert panel was a key ingredient with this approach, highlighting explicitly what these problems were and how we would overcome them. This included agreeing upon definitions of each node before connecting edges between them.

% Although originally multiclass nodes existed, the bayesian network was altered to only include binary class nodes. Each edge between a node had to answer the following questions:
% \begin{enumerate}
%         \item Are the nodes in the BN the right ones?
%         % \item Are the state spaces (values) for each node correct?
%         \item Are the arcs right?
% \end{enumerate}
% If the answer to any of the above questions was no; then the structure was not considered sufficiently defined. Although we explicitly defined the structure of the BN prior to CPT parametarisation. This process continued when adding conditionaly probability values. The entire process of construction iinvolved the steps:
% \begin{enumerate}
%         \item exposing the panel to a strawman argument/model/definition
%         \item Outlining the model and the process involved in defining the structure of a BN
%         \item The expert panel reviewing possible nodes and arcs and definitions
%         \item Defining their own structure, node or term.
%         \item Agreeing upon the final definition, structure or model.
% \end{enumerate}
% \subsubsection{Trying to build the full model all at once}

% Korb & Nicholson say that it is nearly impossible to build a complex BN all in one go. They recommend:
% \begin{enumerate}
%         \item dividing models into subcomponents
%         \item breaking down the problem into a single target variable
%         \item reducing the scope of the problem
%         \item Setting a single time frame for the problem
% \end{enumerate}
% The strawman was presented as three subcomponents that pertained to the triple bottom line's environment, economy and social aspects.
% Within the first workshop it was agreed on by the expert panel to reduce the scope from a triple bottom line to only reviewing the environmental impacts of vineyards. This also reduced the BN to a single terminal node. It was further decided to create the BN as a single season to limit its complexity.

% \subsubsection{The problem}
% \subsubsection{Not understanding the problem context, complexity without value.}
% It is crucial to gain a clear understanding of the problem and its context. This can be seen as answering the following questions:
% \begin{enumerate}
%         \item what do you want to reason about?
%         \item What dont you know?
%         \item What information do you have?
%         \item What do you know?
% These questions are well addressed in prior research. The creation of baseline models showed strong linear relationships between many variables. The creation of XGBoosted trees uncovered the ability to well inform any particular variable but with no real causal structure or understandability. here we seek to pursue causality and link these variables together in a way that is more aligned with a decision support structure than purely as a predictive exercise.
% \subsubsection{Complexity without value}
% A very common impulse, when something is known about the problem, is to want to put it in the model. But including everything known, just because it is known, simply adds complexity to the model without adding any value (and in fact often reduces value). Instead, the knowledge engineer must focus on the problem:
% "Which of the known variables are most relevant to the problem?"
% - This issue in its the simplest form has attempted to be overcome through trying to mediate the workshop and inform experts of the potential problem that will come with a cumbersome model.
% \end{enumerate}

% \subsubsection{Structure - Nodes}
% The list below is each of the problems, which can be addressed together in some fashion as the approaches of solving them overlap.
% \begin{enumerate}
%         \item Getting the node values wrong
%         \item Node values aren't exhaustive
%         \item Node values aren't mutually exclusive
%         \item Incorrect modelling of mutually exclusive outcomes
%         \item Trying to model fuzzy categories
%         \item Confusing state and Probability
%         \item Confusion about what the node represents
% \end{enumerate}
% Two major strategies were employed to overcome these problems. Tying nodes explicitly to a data source that corroborated the definition and state in some manner as the node. For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.

% \subsubsection{Structure Arcs}
% \subsubsection{Getting the arc directions wrong}
% Arc directions are commonly wrong for the following reasons:
% \begin{enumerate}
%         \item Modelling reasoning rather than causation
%         \item Inverting cause and effect
%         \item Missing variables
% \end{enumerate}
% To note: Korb and Nicholson do not actually suggest a method for overcoming these problems. There is an inherint risk in creating a model and not having knowledge of a missing variable or of a causation. It is important to acknowledge that there is always a possibility that causation is mixed up with reasoning, and that not all variables are always known.
% \subsubsection{Too many parents}
% Sometimes it is unavoidable that a node is affected by many factors, or other nodes. There are some methods to help overcome this such as divorcing, in which a node is created to capture the cumulative affects of several parents on a child. This technique was employed in the creation of the structure of the BN with the expert panel.

% \subsubsection{Parameters}
% \subsubsection{Experts estimates of probabilities are biased}
% \begin{enumerate}
%         \item Overconfidence: The attribution of higher than justifiable probabilities to nodes/events.
%         \indent The tendency to attribute higher than justifiable probabilities (\citep{lichtensteinCalibrationProbabilitiesState1982} 
%         \item Anchoring: The tendency towards higher/lower based off of an arbitrary point of comparison. "Anchoring" people at a higher or lower than normal prediction because of some assumption or example  \citep{kahnemanPsychologyPrediction1973}.
%         \item Availability: The assessing of an event as more probable than is justifiable becaues it is more memorable or noticeable \citep{tverskyJudgmentUncertaintyHeuristics1974}.

% \end{enumerate}
% We have attempted to overcome this with two methods. A diverse and varried expert panel. Those participanting have experience in multiple vineyards as managers and other duties as well as the panel itself having varied manager/owners from different regions and scale. With some experts being more specialised in specific areas such as agro-chemicals.
% \subsubsection{Inconsistent probabilities}
% The collection of probabilities for when the CPT is large can result in inconsistent probabilities. The collection of probabilities at different times or if probabilities are supplied by different experts can result in inconsistent probabilities as well.
% The use of desciptors such as very high or low can be of assistance \cite{vandergaag2013elicit}. In this study we overcame this through the use of worded response such as high and low. We then assigned probabilities to those broader cases. We had every expert agree upon each of the probabilities so that they could argue for or against any particular bias and so that the probabilities would even out to a more broader applicability, across all of the experts experiences.
% % \item Inconsistent "filling in" of large CPTs:
% -       -       - Being dead certain.
% \subsubsection{Incoherent probabilities (not summing to 1)}
% We used software that automatically detected incoherent probabilities when filling in the CPT values to overocme this problem.
% \subsubsection{Being dead certain}
% It is important that we limit over confidence (A quote form mark twain was used in the korb and Nicholson). 
% Our best defence against this was to use multiple experts with different experiences and to challenge them when something was certain. To ask why and to check in about their thoughts.

% \citep{morganUncertaintyGuideDealing1990}
% Two attributes of good elicitation process are:
% \begin{enumerate}
%         \item The expert should be apprised of what is known about the process, especially the nearly universal tendency to overcomefidence and other forms of bias. In order to avoid some problems, values should be elicited in random order and the expert not given feedback on how the different values fit together until a complet set has been elicited.
%         \item The elicitation process is not simply one of requesting and recording numbers but also one of the refining the definitions of variables and terms to be used in the model. What values are elicited depends directly upon the interpretation of terms and these should be made as explicit as possible and recorded during the elicitation. This is part of the process management described earlier.
% \end{enumerate}
% -

% \citep{Boneh2021} Boneh, T. (2010). Ontology and Bayesian decision networks for supporting the meterological forecasting process. Ph. D thesis, Clayton School of infomration technology, Monash university
% Boneh 2010 describe Knowledge Engineering with Bayesian Networks (KEBN) as occurring in a 4 stage life cycle:
% - Bayesian Network Structure
% - Probability Parameters
% - Decision Structure
% - Utilities Preference

% Pitchforth \citep{pitchforthProposedValidationFramework2013} agrees with this style of structure naming these steps as:
% - Structure
% - Discretisation
% - Parametarisation
% - Model behaviour
% - Validation

% Korb & Nicholson have a similar view to Pitchforth. utilising a waterfall style developemental approach which include 5 stages:
% - Building the BN
% -       - Structure
% -       - Parameters
% -       - Preferences
% - Validation
% -       - Sensitivity Analysis
% -       - Accuracy testing
% - Field testing
% -       - Alpha/Beta testing
% -       - Acceptance testing
% - Industrial use
% -       - Collection of Statistics
% - Refinement
% -       - Updating procedures
% -       - Regression testing

% Where discretisation and validation are additional steps to assign intervals to continuous factors (discretisation) and to ensure the models appropriateness (validation)

% With validation incorporating the expert scrutiny of the models begaviour for scenarios, as well as comparing this to both data and other literature.

% \subsubsection{Structure and Conditional Probabilities}

% \subsubsection{Validation}

% \citep{korbBayesianArtificialIntelligence2011}

% % Abstract

% 1. Introduction to Methodology

%     Brief overview of the research approach and the rationale behind using a Bayesian Network (BN) model for sustainability assessment in viticulture.
%     Mention of the collaborative expert elicitation process and the sequential workshops that shaped the model development.

% 2. Identification of Sustainability Indicators

%     Description of the process for selecting sustainability indicators, including the use of data from Sustainable Wine Australia.
%     Criteria for indicator selection, focusing on relevance to environmental, economic, and social dimensions of sustainability in winegrowing.

% 3. Expert Elicitation Process

%     Overview of the expert panel composition and the expertise represented.
%     Objectives and structure of the expert elicitation process, highlighting the series of workshops conducted.

% Workshop 1: Variable Review and Straw Man Model Introduction

%     Objectives: To agree on the sustainability indicators and introduce the initial straw man model.
%     Activities: Discussion on indicator relevance and definitions; presentation of the straw man model.
%     Outcomes: Agreement on initial set of variables and conceptual understanding of the model's direction.

% Workshop 2: Model Structure Refinement and Interpolation Method Introduction

%     Objectives: To refine the model's structure and address the complexity of CPTs through an interpolation method.
%     Activities: Examination of variable relationships; identification of complex CPTs; proposal of the linear interpolation method.
%     Outcomes: Revised model structure; decision to develop and implement the interpolation method for complex CPTs.

% Workshop 3: Finalization of CPTs and Case Study Selection

%     Objectives: To finalize CPT values using the interpolation method and select a case study for model application.
%     Activities: Presentation and application of the interpolation method; finalization of CPT values; selection of the Coonawarra wine region for the case study.
%     Outcomes: Completion of model parameterization; selection of case study region emphasizing the model's practical application.

% 4. Development and Implementation of the Interpolation Method

%     Detailed explanation of the linear interpolation method developed to manage the complexity of CPTs for variables with extensive connections.
%     Justification for choosing this method and its anticipated impact on the model's usability and accuracy.

% 5. Case Study Application: Coonawarra Wine Region

%     Rationale for selecting the Coonawarra wine region as a case study to apply and test the BN model.
%     Brief description of how the model was applied to this specific context, including any regional data used and adjustments made for the case study.

% 6. Model Validation

%     Overview of the validation process employed to ensure the accuracy and reliability of the BN model.
%     Description of internal and external validation measures, including expert review and comparison with independent datasets.

% 7. Conclusion

%     Summary of the methodological approach, emphasizing the collaborative expert elicitation process and the innovative solutions developed for model construction and parameterization.
%     Brief mention of the significance of the methodology for sustainability assessment in viticulture and potential implications for future research and practice.

@@

% \subsection{Results notes}

% % =================================
% Structuring the Results Section Based on These Questions:
% Introduction to Results

%     Content: Briefly restate the refined research questions.
%     Explanation: Explain the approach to answering these questions using the BN model and CPT values.

% Primary Factors Identification

% Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?

%     Content: Present the primary factors identified through your analysis.
%     Data: Use the rigorous definitions and the generic BN to highlight these factors.
%     Figures/Tables: Include a table or figure showing the key factors and their relative importance.

% Quantitative Measurement and Analysis

% Question: How can these key factors be quantitatively measured and analyzed to assess their contributions to sustainability in the Australian winegrowing industry?

%     Content: Describe the methods used to measure and analyze the key factors.
%     Data: Show measurements and analytical results from the CPT values in the specific BN models.
%     Figures/Tables: Include charts or tables showing the measurements and analyses.

% Relationships Between Factors

% Question: What are the direct and indirect relationships between these key factors and environmental sustainability in the Australian winegrowing industry?
